Datasheet for 'Beyond Capacity: Analyzing Shelter Use and Government Responses to Homelessness in Toronto

### 2024-03-16 paper/datasheet_template.qmd
Completed data sheet

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

>>>>

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The study analyzed shelter occupancy and capacity data from the City of Toronto's open data platform using R and tools from the tidyverse ecosystem. Data pre-processing, cleaning, and labeling were performed using various R packages, such as dplyr, readr, model summary, janitor, tibble, and ggplot2. The study did not detail specific pre-processing steps, but mentions data manipulation and reading from external sources. However, the document does not mention specific pre-processing techniques for natural language processing and computer vision tasks.

2. *Was the "raw" data saved in addition to the pre-processed/cleaned/labeled data (for example, to support unanticipated future uses)? Ifso, please provide a link or other access point to the "raw" data.*
  - No

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- https://cran.r-project.org/bin/windows/base/
4. *Any other comments?*
	- No

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The study used a dataset to analyze shelter usage trends in Toronto in 2022, focusing on average rates, program models, and capacity needs. A Bayesian analysis model was used to investigate occupancy patterns and service utilization. The findings revealed seasonal trends, peaking during colder months, and differences between emergency and transitional shelter types. The data's use informs policy decisions and enhances support for homeless populations in Toronto.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- We have github link https://github.com/Sinanma/shelter_in_Toronto, we set the access to public.
3. *What (other) tasks could the dataset be used for?*
	- No
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The dataset focuses on shelter occupancy rates, service user counts, and capacity metrics in Toronto's shelter system during 2022. However, it may not fully capture the diversity of the homeless population, potentially underrepresenting certain groups. To mitigate risks, dataset consumers should critically evaluate the dataset, engage with community organizations, follow ethical guidelines, and acknowledge the dataset's limitations when interpreting results and making policy recommendations. This will ensure decisions prioritize equity and the well-being of all community members.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- No

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The document describes an open access dataset that can be found in a public GitHub repository. It is meant to be shared with policymakers, researchers, and other people who are interested. This method encourages people to work together, repeat experiments, and do new analyses. It also stresses ethical, responsible data use, and privacy issues. Users are asked to follow the rules and terms of service so they can contribute positively to the ongoing conversation about homelessness and stable housing.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed via GitHub, a platform for easy access, sharing, and collaboration on code and datasets. It supports version control, issue tracking, and discussion among users. The document does not mention if the dataset has a Digital Object Identifier (DOI), but users can find information about DOIs in GitHub repositories or academic publications3.
3. *When will the dataset be distributed?*
	- The document states that the dataset is available on GitHub, accessible to the public as of the study's publication. Users can access the dataset by visiting the provided link, but should check the repository for updates and changes, as open-source projects can be dynamic. Reviewing the commit history or release section can provide insights into its development.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The document lacks specifics about the dataset's copyright or intellectual property license, as well as any terms of use or fees. However, the the open Creative Commons licenses, which allow varying degrees of reuse and redistribution, are commonly used for academic and research datasets. Users should visit the relevant GitHub repository to review licensing information, such as attribution and restrictions. They are encouraged to consult the dataset's GitHub repository for the most up-to-date licensing terms, which will ensure ethical and legal use.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- The document lacks specifics about the dataset's copyright or intellectual property license, as well as any terms of use or fees. Open Creative Commons licenses, which allow varying degrees of reuse and redistribution, are commonly used for academic and research
datasets. Users should visit the relevant GitHub repository to review licensing information, such as attribution and restrictions. They are encouraged to consult the dataset's GitHub repository for the most up-to-date licensing terms, which will ensure ethical and legal use.
7. *Any other comments?*
	- No

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- OpenDataToronto platform.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- tsssdata@toronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The document doesn't specify specific updates for the dataset, but it suggests that it can be made by creators or contributors at any time, tracked through GitHub's version control system. Communication about updates could be facilitated through commit messages, GitHub's release feature, issues, discussions, or README file updates. Users are encouraged to follow the repository for updates.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The document doesn't specify the support for older dataset versions or communication strategies for changes. GitHub allows for archival and access of older versions through commit history and releases, but dataset creators are responsible for actively supporting or updating them. If support ceases, communication may occur through README files, releases announcements, or issues discussions. Users should stay engaged with the repository for updates.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The document does not specify support for older dataset versions or communication strategies for change. However, GitHub allows for the archival and access of older versions via commit history and releases, but dataset creators must actively support or update them. If support is discontinued, communication may occur via README files, release announcements, or issue discussions. Users should stay connected to the repository for updates.
8. *Any other comments?*
	- No
